\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage{multicol}

% Comment the following line to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[sc,osf]{mathpazo}

% In practice, I use the following font packages instead of mathpazo.
% beramono provides a nice fixed-width font. xagaramon uses the
% (commercial) Adobe Garamond font.
%\usepackage[scaled=0.75]{beramono}
%\usepackage[osf]{xagaramon}

% Set your name here
\def\name{Craig G. Weinschenk}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name} \\
\noindent\rule{17cm}{0.4pt}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}[t]{0.5\textwidth}
  4620 N Park Ave 302E \\
  Chevy Chase, MD  20815\\
  Date of Birth: September 7, 1984 \\
  Citizenship: United States
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  Phone: (732) 266-7757 \\
  Email: \href{mailto:craig.weinschenk@ul.com} {\tt craig.weinschenk@ul.com}\\

\end{minipage}

\section*{Education}

\begin{itemize}
  \item Ph.D. Mechanical Engineering, The University of Texas at Austin, 2011
    \begin{itemize}
      \item \textit{Dissertation:} Experimental and Computational Characterization of Strong Vent Flow Enclosure Fires
    \end{itemize}

  \item M.S. Mechanical Engineering, The University of Texas at Austin, 2007
    \begin{itemize}
      \item \textit{Thesis:} A Study of Firefighter Compliance to Ventilation Standard Operating Guidelines and Development of a Computational Model of a Ventilation Fan
    \end{itemize}

  \item B.S. Mechanical Engineering, Rowan University, 2006
\end{itemize}

\section*{Professional Experience}
Research Engineer \hfill October 2016 - Present \\
{\bf UL FSRI} \hfill Columbia, MD \vskip3pt
Full-scale fire testing for improving firefighter safety, fire modeling to improve knowledge on fire development and thermal conditions for firefighters, community risk and fire department performance modeling for FireCARES and NFORS projects. \\

Research Engineer \hfill February 2016 - October 2016 \\
{\bf Jensen Hughes} \hfill Rockville, MD \vskip3pt
Community risk and fire department performance modeling for Fire CARES project. Coupled FDS and Abaqus modeling for structural fire analysis. Development of network based fire model coupled to structural failure model.\\

Research Fire Protection Engineer \hfill August 2011 - February 2016 \\
{\bf National Institute of Standards and Technology} \hfill Gaithersburg, MD \vskip3pt
A principal developer of NIST's Fire Dynamics Simulator (FDS). Implemented, verified, and validated a partially stirred batch reactor combustion model into FDS designed to improve under-ventilated combustion modeling. Conducted fire modeling studies to provide insight on the fire development and thermal conditions during firefighter fatality and injury incidents. Conducted full-scale field experiments aimed at improving firefighter safety and tactics. \\

Graduate Research Assistant \hfill August 2006 - July 2011 \\
{\bf The University of Texas at Austin} \hfill Austin, TX \vskip3pt
Constructed fire-hardened, single-compartment scale experimental facility and developed data acquisition/instrumentation infrastructure. Conducted research analyzing the impact of forced and natural ventilation in compartment fires: experimental and numerical studies. Participated in full-scale wildland fire experiments. \\

% Undergraduate Research Assistant \hfill May 2004 - August 2004; May 2006 - July 2006 \\
% {\bf Rowan University} \hfill Glassboro, NJ \vskip3pt
% Conducted on-scene, post-incident investigations regarding vehicle impacts with guiderails throughout the state of New Jersey. Built investigation documents and safety produces. Developed database to catalog investigations. \\

% Engineering Intern \hfill May 2005 - August 2005 \\
% {\bf Bombardier Transportation (River LINE Services)} \hfill Camden, NJ \vskip3pt
% Developed solutions for safely and efficiently greasing rail lines and for cleaning train wheels during active service to ensure shunting consistency. Developed text and audible indicators for modified service routes. \\

\clearpage

\section*{Publications}
\begin{enumerate}
\item Madrzykowski, D., and Weinschenk, C. Understanding and Fighting Basement Fires. Technical Report, Underwriters Laboratories Firefighter Safety Research Institute, Columbia, MD, April 2018.
\item Weinschenk, C., Stakes, K., and Zevotek, R. Impact of Fire Attack Utilizing Interior and Exterior Streams on Firefighter Safety and Occupant Survival: Air Entrainment. Technical Report, Underwriters Laboratories Firefighter Safety Research Institute, Columbia, MD, December 2017.
\item Weinschenk, C., Stakes, K., and Zevotek, R. Impact of Fire Attack Utilizing Interior and Exterior Streams on Firefighter Safety and Occupant Survival: Water Mapping. Technical Report, Underwriters Laboratories Firefighter Safety Research Institute, Columbia, MD, December 2017.
\item Weinschenk, C., Madrzykowski, D., Stakes, K, and Willi, J. Examination of Compressed Air Foam (CAF) for Interior Firefighting. NIST Technical Note 1927, US Department of Commerce, National Institute of Standards and Technology, January 2017.
\item Willi, J.M, Madrzykowski, D., and Weinschenk, C. Impact of Hose Streams on Air Flows inside a
Structure, NIST Technical Note 1938, National Institute of Standards and Technology, Gaithersburg, MD, October 2016.
\item Weinschenk, C.G., Overholt, K.J., and Madrzykowski, D. Simulation of an Attic Fire in a Wood Frame Residential Structure, Chicago, IL. Fire Technology 52(6) (2016): 1629-1658.
\item Zhang, C., Silva, J. G., Weinschenk, C., Kamikawa, D., and Hasemi, Y. Simulation methodology for coupled fire-structure analysis: modeling localized fire tests on a steel column. Fire Technology, 52(1) (2016): 239-262.
\item Weinschenk, C.G., Overholt, K.J., and Madrzykowski, D., Simulation of a Residential Wind Driven Basement Fire - Riverdale Heights, MD, NIST Technical Note 1870, National Institute of Standards and Technology, Gaithersburg, MD, February 2015.
\item Overholt, K.J., Weinschenk, C.G., and Madrzykowski, D., Simulation of a Fire in a Hillside Residential Structure - San Francisco, CA, NIST Technical Note 1856, National Institute of Standards and Technology, Gaithersburg, MD, December 2014.
\item Weinschenk, C.G., Overholt, K.J., and Madrzykowski, D., Simulation of the Dynamics of an Attic Fire in a Wood Frame Residential Structure - Chicago, IL, NIST Technical Note 1838, National Institute of Standards and Technology, Gaithersburg, MD, August 2014.
\item  Weinschenk, C. and Ezekoye, O.A., Characterization of a CFD Thermocouple Model Subjected to Stochastic Environmental Forcing using Moment Based Analysis, ASME Journal of Thermal Science and Engineering Applications 5 (4), 10, 2013
\item McGrattan, K., Hostikka, S., McDermott, R., Floyd, J., Weinschenk, C., and Overholt, K., Fire Dynamics Simulator, Technical Reference Guide, National Institute of Standards and Technology, Gaithersburg, Maryland, USA, and VTT Technical Research Centre of Finland, Espoo, Finland, Sixth edition, September 2013. Vol. 1: Mathematical Model; Vol. 2: Verification Guide; Vol. 3: Validation Guide; Vol. 4: Configuration Management Plan.
\item McGrattan, K., Hostikka, S., McDermott, R., Floyd, J., Weinschenk, C., and Overholt, K., Fire Dynamics Simulator, User's Guide, National Institute of Standards and Technology, Gaithersburg, Maryland, USA, and VTT Technical Research Centre of Finland, Espoo, Finland, Sixth edition, September 2013.
\item Averill, J., Moore-Merrell, L., Ranellone, R., Weinschenk, C., Taylor, N., Goldstein, R., Santos, R., Wissoker, D., and Notarianni, K., Report on High-Rise Fireground Field Experiments,Technical Note 1797. National Institute of Standards and Technology Gaithersburg, Maryland. April 2013.
\item Weinschenk, C., Beal, C., and Ezekoye, O.A., Insights Into Modeling of a Fan Driven Firefighting Tactic Using Nonreacting Flow Data, Journal Society of Fire Protection Engineering. January 2011 Vol. 21
\item Weinschenk, C., Ezekoye, O.A. and Nicks, R., Analysis of Fireground Standard Operating Guidelines/Procedures Compliance for Austin Fire Department, Fire Technology, 1572-8099, October 04, 2007.
\end{enumerate}

%\clearpage

\section*{Conference Proceedings}
\begin{enumerate}
\item McDermott, R., and Weinschenk, C., A Partially-Stirred Batch Reactor Model for Under-Ventilated Fire Dynamics, Bulletin of the American Physical Society 58, November 2013
\item Weinschenk, C. , Forney, G., Averill, J., and Ranellone, R. A Method to Evaluate Alternative Fire Safety Strategies, 13th International Conference and Exhibition on Fire Science and Engineering, Interflam 2013, East Windsor, UK. June 23-26 2013.
\item Floyd, J., Weinschenk, C., and McDermott, R. A Generic Combustion Modeling and Species Transport Framework for Fire Dynamics Simulator, 13th International Conference and Exhibition on Fire Science and Engineering, Interflam 2013, East Windsor, UK. June 23-26 2013.
\item Weinschenk, C., Upadhyay, R., and Ezekoye, O.A., Comparison of a Partially Stirred Reactor Model and a Perfectly Stirred Reactor Model for Large Vent Flow Fires, U.S. Joint National Combustion Meeting, Atlanta, GA March 2011.
\item Weinschenk, C. and Ezekoye, O.A., Analysis of Thermocouple Response to Turbulent Radiating Environments, ASME/JSME 2011 8th Thermal Engineering Joint Conference, March 13-17, 2011.
\item  Kokel, P., Weinschenk, C., and Ezekoye, O.A., Evaluation of Directional Flame Thermometer for Real-time Inversion of Heat Flux, International Heat Transfer Conference 14. August 8-13 2010.
\end{enumerate}

\section*{Conference Talks}
\begin{enumerate}
\item Firehouse High-Rise Fire and Life Safety Summit, August 2017, Minneapolis, MN, {\em NIST Fireground Study: High-Rise and FireCARES}
\item IAFF Redmond Symposium Occupational Health \& Hazards of the Fire Service, August 2017, Vancouver, BC {\em The FireCARES and NFORS Big Data Projects}
\item International Structural Fire Conference, September 2016, Warsaw, Poland, {\em Fire Modeling with FDS, From Development to Application}
\item NFPA Smart Solutions Showcase on Big Data, NFPA Conference and Expo, June 2016, Las Vegas, NV
\item IAFF Redmond Symposium Occupational Health \& Hazards of the Fire Service, August 2015, National Harbor, MD {\em Chicago, IL, In Memory of Capt. Herbie Johnson}
\item IAFF Redmond Symposium Occupational Health \& Hazards of the Fire Service, August 2015, National Harbor, MD {\em Risk vs. Response: The FireCARES Project}
\item NIST Fire Fighting Research \& Practice: From the Lab to the Street, August 2015, Gaithersburg, MD {\em Fire Dynamics Simulator for LODD/LODI Simulations}
\item NIST Fire Fighting Research \& Practice: From the Lab to the Street, August 2015, Gaithersburg, MD {\em Heat Transfer through Personal Protective Equipment}
\item NFPA Conference and Expo, June 2015, Chicago, Il {\em Transient Thermal Response of Fire Fighter Clothing and Helmets in Heated Flow Path Conditions}
\item Fire Department Instructors Conference (FDIC), April 2014, {\em UL-NIST Live Fire Dynamics for Fire Officers - Hot Class}
\item Ontario Professional Fire Fighters Association Health and Safey Conference, February 2015, Broadcast from Washington, DC {\em Fire Dynamics for the Fire Service}
\item IAFF Affiliate Leadership Training Summit, January 2015, Anaheim, CA {\em NFPA 1710 and NIST Fireground Studies: Residential \& High-Rise}
\item Fire and Evacuation Modeling Technical Conference August 2014, Gaithersburg, MD {\em A Partially-Stirred Batch Reactor Model for Under-Ventilated Fire Dynamics}
\item IAFF Affiliate Leadership Training Summit / N-FORS Stakeholder Meeting, January 2014, Orlando, FL {\em NIST Fireground Studies: Residential \& High-Rise}
\item IAFF Redmond Symposium Occupational Health \& Hazards of the Fire Service, August 2013, Denver, CO {\em NIST High-Rise Fireground Study}
\item Firehouse Expo, July 2013, Baltimore, MD {\em NIST High-Rise Fireground Study}
\item Metropolitan Fire Chiefs Annual Conference, April 2013, Phoenix, AZ {\em NIST High-Rise Fireground Study}
\item IAFF Affiliate Leadership Training Summit, January 2013, Phoenix, AZ {\em NIST High-Rise Fireground Study}
\item FM Global Open Source CFD Fire Modeling Workshop, May 2012, Boston, MA {\em A Lumped Species Approach to Modeling Simple Chemistry in Under-Ventilated Fires}
\end{enumerate}

\clearpage

% \section*{Technical Committees}

% Principal on the NFPA Technical Committee on Structural and Proximity Fire Fighting Protective Clothing and Equipment (FAE-SPF) (2015) \\
% \vskip1pt
% Alternate on the NFPA Technical Correlating Committee on Fire and Emergency Services Protective Clothing and Equipment (FAE-AAC) (2015) \\

\section*{Skills}
NIST Fire Dynamics Simulator (FDS) \\
CFAST Zone Model \\
Small-Scale and Large-Scale Fire Experiments \\
Fire Instrumentation and Data Collection \\
Python / NumPy / matplotlib / Pandas / Bokeh / plotly \\
Fortran / C++ / Matlab \\
LabVIEW \\
\LaTeX \\
Subversion / Git \\

\section*{Honors, Awards, \& Fellowships}

Department of Commerce Silver Medal, 2016 \\
NRC Postdoctoral Fellow, NIST, 2011-2013 \\
Continuing Bruton Fellowship, The University of Texas at Austin, 2010 \\
Thrust 200 Graduate Fellowship in Engineering, The University of Texas at Austin, 2006-2010 \\
University Preemptive Fellowship, The University of Texas at Austin, 2006 \\
Mechanical Engineering Medallion, Rowan University, 2006 \\
Outstanding Scholar Fellowship, Rowan University, 2002-2006 \\
Eagle Scout - BSA Troop 83, 2001 \\

\section*{Research Interests}
Fire modeling/simulation and fire dynamics \\
Turbulent numerical combustion \\
Verification and validation of fire models \\
Firefighter hose stream and ventilation tactics \\
Community risk scale modeling related to the fire service \\
Scientific and high performance computing, data analytics \\
PDF evolution using moment methods \\

\bigskip

\end{document}

